LEGWORK: LISA Evolution and Gravitational Wave Orbit Kit

### 2021-11-02 src/ms.tex
change bib file name
uncomment the last figure
change back to fontawesome5 icons
remove links to jupyter notebooks

\usepackage{physics}
\usepackage{mathtools}
\usepackage{etoolbox}
\usepackage{fontawesome}

@@

% icons and links
\newcommand{\docsIcon}{{\color{\lwColour}{\faBook}}}
\newcommand{\docsLink}[1]{\href{#1}{\docsIcon}}

\newcommand{\tutorialIcon}{{\color{\lwColour}{\faBook}}}
\newcommand{\tutorialLink}[1]{\href{#1}{\tutorialIcon}}

\newcommand{\notebookIcon}{{\color{\lwColour}{\faBook}}}
\newcommand{\notebookLink}[1]{\href{#1}{\notebookIcon}}

@@

\lw{} can be installed with pip or obtained from the GitHub repository \href{https://github.com/TeamLEGWORK/LEGWORK}{\faGithub}\footnote{\url{https://github.com/TeamLEGWORK/LEGWORK}}. All examples shown in this paper and code to reproduce the figures are available in the repository. Throughout this paper a \tutorialIcon{} icon in a section links to a related online tutorial and a \notebookIcon{} icon links to a Jupyter notebook with related code examples. Instructions for installation and basic usage are provided in the online documentation\footnote{\url{https://legwork.readthedocs.io/en/latest/}} which contain the most up-to-date instructions.

@@

\section{Use cases}\label{sec:example-uses}
In this section, we demonstrate \lw{}'s range of capabilities through a series of example use cases. The plots and results in each subsection are reproduced directly in online demos in the \lw{} documentation, which are each based on individual Jupyter notebooks. These are linked at the start of each subsection with the \tutorialIcon{} and \notebookIcon{} icons respectively.

\subsection{Computing the SNR of a binary system\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/BasicSNRCalculation.html} \notebookLink{https://github.com/TeamLEGWORK/LEGWORK/blob/main/docs/demos/BasicSnrCalculation.ipynb}}{}}

@@

\subsection{Horizon distance\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/HorizonDistance.html} \notebookLink{https://github.com/TeamLEGWORK/LEGWORK/blob/main/docs/demos/HorizonDistance.ipynb}}{}}

@@

\subsection{The role of eccentricity\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/TheRoleofEccentricity.html} \notebookLink{https://github.com/TeamLEGWORK/LEGWORK/blob/main/docs/demos/TheRoleofEccentricity.ipynb}}{}}\label{sec:eccentricity_role}

@@

\subsection{Compare different gravitational wave detectors\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/CompareSensitivityCurves.html} \notebookLink{https://github.com/TeamLEGWORK/LEGWORK/blob/main/docs/demos/CompareSensitivityCurves.ipynb}}{}}

@@

\subsection{Track SNR of a binary over time\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/SNROverTime.html} \notebookLink{https://github.com/TeamLEGWORK/LEGWORK/blob/main/docs/demos/SNROverTime.ipynb}}{}}

@@

\bibliography{references}
\bibliographystyle{aasjournal}

>>>>

\usepackage{physics}
\usepackage{mathtools}
\usepackage{etoolbox}

@@

% icons and links
\newcommand{\docsIcon}{{\color{\lwColour}{\faFileCode}}}
\newcommand{\docsLink}[1]{\href{#1}{\docsIcon}}

\newcommand{\tutorialIcon}{{\color{\lwColour}{\faLaptopCode}}}
\newcommand{\tutorialLink}[1]{\href{#1}{\tutorialIcon}}

@@

\lw{} can be installed with pip or obtained from the GitHub repository \href{https://github.com/TeamLEGWORK/LEGWORK}{\faGithub}\footnote{\url{https://github.com/TeamLEGWORK/LEGWORK}}. All examples shown in this paper and code to reproduce the figures are available in the repository. Instructions for installation and basic usage are provided in the online documentation\footnote{\url{https://legwork.readthedocs.io/en/latest/}} which contain the most up-to-date instructions.

@@

\section{Use cases}\label{sec:example-uses}
In this section, we demonstrate \lw{}'s range of capabilities through a series of example use cases. The plots and results in each subsection are reproduced directly in online demos in the \lw{} documentation, which are each based on individual Jupyter notebooks. These tutorials are linked at the start of each subsection with the \tutorialIcon{} icon.

\subsection{Computing the SNR of a binary system\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/BasicSNRCalculation.html}}{}}

@@

\subsection{Horizon distance\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/HorizonDistance.html}}{}}

@@

\subsection{The role of eccentricity\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/TheRoleofEccentricity.html}}{}}\label{sec:eccentricity_role}

@@

\subsection{Compare gravitational wave detectors\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/CompareSensitivityCurves.html}}{}}

@@

\subsection{Track SNR of a binary over time\texorpdfstring{ - \tutorialLink{https://legwork.readthedocs.io/en/latest/demos/SNROverTime.html}}{}}

@@

\bibliography{bib}
\bibliographystyle{aasjournal}
